An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-10-02 paper.tex
Add summary for §5.3

\todo{summarise hierarchy results}

>>>>

These findings presented in \S\ref{sec:org-dyn:hierarchy:rq2} --
\S\ref{sec:org-dyn:hierarchy:rq4} suggest that the negative association of
power distance is not as pronounced for the IETF as the literature finds
for traditional commercial organisations. In fact, the facilitation by
working group chairs of regular participants suggests the high levels
actively encourage lower level participation in discussion. 
Moreover, combining this with the finding that the organisational hierarchy
has a diffused structure (\S\ref{sec:org-dyn:hierarchy:rq1}), with the
potential problems this may cause for lower levels, suggests that
collaboration between hierarchy levels is high within the IETF.

As the IETF is voluntary and collaborative in its mission, this suggests
that the their process for tackling the problems caused by a diffused
hierarchy and power distance have worked well. One suggested improvement
for the IETF is to encourage working group chairs to get involved in more
group discussion in the mailing lists. This may help to boost their level
of \textit{Philanthropy}, \textit{Community} and Triangle motifs, which are
indicators of healthy discussion. However, we do not advocate for our
analysis techniques to be the only metrics maximised for.  Moreover, these
conclusions come from analysis of only communication structure not content.
A future look into content may elucidate differing relationships between
hierarchy levels.
